FocalGstar

### 2017-06-15 analysis.Rmd
update size of metric-example image

## Example of Parent-Child Clumping Difference
```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
r <- rast[[ZOOMLEVEL]]
st1 <- GetisOrdStandardStats(r)
st2 <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
plot_clumping_diff(r, st1, ZOOM_WMATRIX_SIZE, 29)
plot_clumping_diff(r, st2, ZOOM_WMATRIX_SIZE, 29)
```

>>>>

## Example of Parent-Child Clumping Difference
```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=5, fig.height=4.1}
r <- rast[[ZOOMLEVEL]]
st1 <- GetisOrdStandardStats(r)
st2 <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
plot_clumping_diff(r, st1, ZOOM_WMATRIX_SIZE, 29)
plot_clumping_diff(r, st2, ZOOM_WMATRIX_SIZE, 29)
```
